Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-19 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Changes to draft

```{r}
my_hurricanes <- c("Floyd-1999", 
                   "Irene-2011", 
                   "Lee-2011", 
                   "Ike-2008",
                   "Allison-2001")
#pdf("validate_precip.pdf")
#for(hurricane in my_hurricanes){
        a <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -3)
        a <- map_tracks(storm = hurricane, 
                        plot_object = a)
        b <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -2)
        b <- map_tracks(storm = hurricane, 
                        plot_object = b)
        c <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -1)
        c <- map_tracks(storm = hurricane, 
                        plot_object = c)
        d <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 0)
        d <- map_tracks(storm = hurricane, 
                        plot_object = d)
        e <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 1)
        e <- map_tracks(storm = hurricane, 
                        plot_object = e)
        f <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 2)
        f <- map_tracks(storm = hurricane, 
                        plot_object = f)
        g <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 3)
        g <- map_tracks(storm = hurricane, 
                        plot_object = g)
        precip_plot <- grid.arrange(a, b, c, d, e, f, g, nrow = 2)
        print(precip_plot)
}
#dev.off()
```

>>>>

```{r}
my_hurricanes <- c("Floyd-1999", 
                   "Irene-2011", 
                   "Lee-2011", 
                   "Ike-2008",
                   "Allison-2001")
pdf("validate_precip.pdf", height = 8, width = 12)
for(hurricane in my_hurricanes){
        a <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -3) + theme(legend.position="none")
        a <- map_tracks(storm = hurricane, 
                        plot_object = a, plot_points = FALSE)
        b <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -2)
        b <- map_tracks(storm = hurricane, 
                        plot_object = b)
        c <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -1)
        c <- map_tracks(storm = hurricane, 
                        plot_object = c)
        d <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 0)
        d <- map_tracks(storm = hurricane, 
                        plot_object = d)
        e <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 1)
        e <- map_tracks(storm = hurricane, 
                        plot_object = e)
        f <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 2)
        f <- map_tracks(storm = hurricane, 
                        plot_object = f)
        g <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 3)
        g <- map_tracks(storm = hurricane, 
                        plot_object = g)
        precip_plot <- grid.arrange(a, b, c, d, e, f, g, nrow = 2,
                                    top = textGrob("Title"))
        print(precip_plot)
}
dev.off()
```
